When does vapor pressure deficit drive or reduce evapotranspiration?

### 2018-03-28 doc/paper/vpd_et_paper.tex
forgot concave plot

>>>>

\subsection{Functional form of ET dependence on VPD and its relation to uWUE}

Th theory described in Section \ref{sign_term} indicates that for a given $uWUE$ and $g_1$, the ET dependence on VPD should be concave upward. In other words, there should be some local minima in ET at a critical VPD$_{crit}$, assuming the scaling term (e.g. aerodynamic conductance and $\Delta$) is held fixed. This result warrants futher investigation, because to our knowledge no one has derived the theoretical ecosystem-scale relationship between ET and VPD while controlling for enivironmental conditiions. In particular, from personal communication, there is an apparent lack of consensus over whether the shape of the ET-VPD curve should be concave upward (our result) or concave downward. Given that understanding the ET-VPD relationship of the one-way plant response is absolutely fundamental for hypothesizing about any feedbacks between the land surface and the atmopshere, we analyze why our derived ET-VPD relationship is concave upward, particularly with respect to our use of $uWUE$ to make explicit the relationship betwen GPP, ET, and VPD.
